MS_CNuptake.Rmd

### 2022-07-12 MS_CNuptake.Rmd
MS really submitted

#without age - re-selection - this is best
anpp_leafnpp_dataset <- na.omit(NPP_forest[,c("anpp_leafnpp_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
model3 <- stepwise(anpp_leafnpp_dataset,"anpp_leafnpp_a")
model3[[1]]
model3[[3]]
anpp_leafnpp_model <- (lmer(anpp_leafnpp_a~fAPAR_a+vpd_a+PPFD_a+(1|site_a),data=anpp_leafnpp_dataset)) 
r.squaredGLMM(anpp_leafnpp_model)
AIC(anpp_leafnpp_model)
summary(anpp_leafnpp_model)
r.squaredGLMM(anpp_leafnpp_model)
vif_anpp_leafnpp <- vif((lmer(anpp_leafnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)))

@@

a14 <- gg$gglegend+labs(title = ~paste("gN m"^-2,"yr"^-1))+ white

>>>>

#without age - re-selection - this is best
anpp_leafnpp_dataset <- na.omit(NPP_forest[,c("anpp_leafnpp_a","fAPAR_a","CNrt_a","Tg_a","PPFD_a","vpd_a","site_a")])
model3 <- stepwise(anpp_leafnpp_dataset,"anpp_leafnpp_a")
model3[[1]]
model3[[2]]
model3[[3]]
anpp_leafnpp_model <- (lmer(anpp_leafnpp_a~fAPAR_a+vpd_a+PPFD_a+(1|site_a),data=anpp_leafnpp_dataset)) 
r.squaredGLMM(anpp_leafnpp_model)
AIC(anpp_leafnpp_model)
summary(anpp_leafnpp_model)
r.squaredGLMM(anpp_leafnpp_model)
vif_anpp_leafnpp <- vif((lmer(anpp_leafnpp_a~Tg_a+fAPAR_a+PPFD_a+CNrt_a+age_a+vpd_a+(1|site_a),data=anpp_leafnpp_dataset_age)))

@@

a14 <- gg$gglegend+ white
